---
title: "egworkflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{egworkflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dplyr)
#library(blockstrap)
```
# Introduction to Blockstrap 
Blockstrap is an R package developed for resampling data structures that naturally come in blocks. A common example is the line-listed hospital admission data, where each subject may appear in multiple rows. These rows can be grouped into meaningful units such as a sequence of visits by the same subject that occur close together. We refer to each such grouping as a block.

Blockstrap provides tools to perform a block bootstrap, resampling these blocks rather than resampling individual rows independently as in a traditional bootstrap.

In this document, we demonstrate how to:

- Create an example line-listed dataset in the hospital admission context
- Partition the dataset into blocks
- Perform block bootstrap using slice_block() function

## Generate an example dataset 
For illustration, we use the create_fake_subjectDB() function from the HospitalNetwork package to generate a fake subject database containing admission/discharge records.
```{r}
library(HospitalNetwork)
set.seed(1)
df<- create_fake_subjectDB()
df
```
Here, df contains four columns: 

- `sID`: Subject ID
- `fID`: Facility ID
- `Adate`: Admission date for the visit
- `Ddate`: Discharge date for the visit

## Group rows into blocks 
We define a block as a sequence of visits by the same subject that occur close together, that is, a new block begins when:

- It is the first record for the subject, or
- The difference in days between the previous discharge (`Ddate`) and the current admission (`Adate`) exceeds 40 days

```{r}
df2<- df |>  
  group_by(sID) |>
  mutate( Adate = as.Date(Adate),
          Ddate = as.Date(Ddate)) |>
  arrange(Adate, .by_group= TRUE) |>
  mutate( diff_time = Adate - lag(Ddate),
          is_start = is.na(diff_time) | diff_time > 40,
          idx_within_sid = cumsum(is_start),
          idx_block = as.factor(paste0(sID, "_", idx_within_sid)))

df2
```
The column `idx_block` is a factor that identifies which block each row belongs to. Note that rows that share the identical entries in `idx_block` belong to the same block. 

## Block bootstrap
With the block IDs defined, we use the slice_block() function to perform block bootstrap.


In this example, 

